Lasso_RCI_Response

### 2024-03-25 Lasso_RCI_Response.Rmd
MADE FP AND FINALIZED MODELS!!!!!

                                  #ifelse(OCD_P == 1, "Anxiety",
                                     #felse(OCD_P == 1, "Other",

@@

## Vector of categorical variables that need transformation
catVars <- c("Some_College", "Female" , "Married", "White",
             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D","Substance_D" ,        
             "Psychotic_D", "Other", "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
             "Substance_C", "Other_C" , "No_Co"
             )
## Create a TableOne object
table1_tab_dep <- CreateTableOne(vars = table1_vars_dep, data = Vars_dep,strata ="Depression_Responder",  factorVars = catVars)
table1_tab_dep <- print(table1_tab_dep, formatOptions = list(big.mark = ","))
table1_tab_dep <-data.frame(table1_tab_dep)
table1_tab_dep

@@

# Depression Lasso 
Preparing data for lasso - Anxiety
```{r}
Mothership_lasso_dep <- Mothership_lasso |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(Depression_Responder)
  )

Vars_dep <- Mothership_lasso_dep |>
  select( c(
    Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, 
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, 
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, #Substance_D, Psychotic_D,  
    Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre,
    # RDQ
    rdqPOST_coping:rdqPOST_wbs
  ))

@@

# Fit the final model on the training data
model.min <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
                lambda = cv.lasso.dep$lambda.min)
# Display regression coefficients
coef(model.min)

@@

### Final relaxed lasso- Depression
Minimum- 
```{r}
## install.packages("fuzzySim")
library(fuzzySim) ## For FDR adjusted p values
library(broom) # for tidy regression output
# Old model
# ## min model
#   glm_min_dep <-  
#       glm(
#       #Outcome varaible
#         Depression_Responder ~ 
#       # predictors
#         Married + Days_not_attended_1 + Mood_D + Anxiety_C + Substance_C +
#         CUDOS_pre + CUXOS_pre + rdq_coping_change + rdq_pmh_change + 
#         rdq_func_change,
#       #data
#       data = Vars_dep, 
#       # type of regression : logistic = binary / binomial
#       family = "binomial")
```

```{r}
## min model
  glm_min_dep <-
      glm(
      #Outcome varaible
        Depression_Responder ~
      # predictors
        Days_complete_1 + Days_not_attended_1 + Other + Mood_C + CUDOS_pre +  
        CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
      #data
        data = Vars_dep,
      # type of regression : logistic = binary / binomial
        family = "binomial")

@@

# Left join the FDR adjusted p.value
FP.min.dep <- left_join(FP.min.dep,ADJ.p.values.min.dep, by = join_by(p.values == p.value))
FP.min.dep$type = c("Depression")
FP.min.dep
```
1se -
```{r}

@@

Vars_anx <- Mothership_lasso_anx |>
  select( c(
    Anxiety_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, #Substance_D, Psychotic_D,  
    Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs
  ))

@@

## min model
  glm_min_anx <-  
      glm(
      #Outcome varaible
        Anxiety_Responder ~ 
      # predictors
        Age_1 + Married + Days_complete_1 + Days_not_attended_1 + 
        Anxiety_D + Trauma_D + Substance_C + BPD_Co_C +
        rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
      #data
      data = Vars_anx, 
      # type of regression : logistic = binary / binomial
      family = "binomial")

# Summary of the model
  summary.min.anx      <- summary(glm_min_anx)

@@

# Left join the FDR adjusted p.value
FP.min.anx <- left_join(FP.min.anx,ADJ.p.values.min.anx, by = join_by(p.values == p.value))
FP.min.anx$p.values = round(as.numeric(FP.min.anx$p.values),3)
FP.min.anx$p.adjusted = round(as.numeric(FP.min.anx$p.adjusted),3)
FP.min.anx$type = c("Anxiety")
FP.min.anx

@@

```{r}
#Create order varaible in dataset to keep it the same as the regression

FP_test <- read_csv("~/Downloads/FP.min.anx")

FP_test$order = c(seq(from=2, to=length(FP.min.anx$Variable) + 1,1))

FP_test <- FP_test |>
  mutate(
    sig = ifelse(p.adjusted <= 0.05, 16,1)
  )
FP_test
```

```{r}
FP_test_m <- FP_test |>
  ggplot(aes(y = reorder(Variable, -order), color = as.factor(sig))) +
  #take away background
  theme_classic() +
  #make the forrest plot
  geom_point(aes(x=OR), shape= FP_test$sig,
               # ifelse(FP_test$p.adjusted <= 0.05, 
               #                        16, # colored ones for significant varaibles
               #                        1), # uncolored ones for insignificant varaibles
             size=4,show.legend = FALSE) +
  geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = .4, show.legend = FALSE) +
  geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.35, show.legend = FALSE)+
  scale_color_manual(values = c("darkgrey","red"))+
  #change x axis name
  labs(
    x="Odds Ratio",
    title = "Odds of Anxiety Treatment Non-Response",
    subtitle = "Based on Pre/Post CUXOS Scores in PHP program") +
  #adjust the dimentions. 
  coord_cartesian(ylim = c(1,length(FP_test$Variable) + 1)) +
  #add a line at 1 for reference 
   geom_vline(xintercept = 1, linetype="dashed", alpha = .5) +
  #add anotations to help suggests what each side means.
  annotate("text", x = .8, y = length(FP_test$Variable) + 1, label = "Less Likely", size= 3) +
  annotate("text", x = 1.2, y = length(FP_test$Variable) + 1, label = "More Likely",size= 3) +
  #Git rid of the Y - Axis
    theme(axis.line.y = element_blank(),
        axis.ticks.y= element_blank(),
        axis.text.y= element_blank(),
        axis.title.y= element_blank())

FP_test_m
```

```{r}
FP_test <- FP_test |>
  # round estimates and 95% CIs to 2 decimal places for journal specifications
  mutate(across(
    c(OR, OR_low, OR_high),
    ~ str_pad(
      round(.x, 2),
      width = 4,
      pad = "0",
      side = "right"
    )
  ),
  # add an "-" between HR estimate confidence intervals
  estimate_lab = paste0(OR, " (", OR_low, "-", OR_high, ")")) |>
  # round p-values to two decimal places, except in cases where p < .001
  mutate(p.adjusted_fig = case_when(
    p.adjusted < .001 ~ "<0.001",
    round(p.adjusted, 2) == .05 ~ as.character(round(p.adjusted,3)),
    p.adjusted < .01 ~ str_pad( # if less than .01, go one more decimal place
      as.character(round(p.adjusted, 3)),
      width = 4,
      pad = "0",
      side = "right"
    ),
    TRUE ~ str_pad( # otherwise just round to 2 decimal places and pad string so that .2 reads as 0.20
      as.character(round(p.adjusted, 2)),
      width = 4,
      pad = "0",
      side = "right"
    )
  )) |>
  # add a row of data that are actually column names which will be shown on the plot in the next step
  bind_rows(
    data.frame(
      Variable = "Variable",
      estimate_lab = "Odd Ratio (95% CI)",
      OR_low = "",
      OR_high = "",
      p.adjusted_fig = "p value"
    )
  )

FP_test[14,8] = 1
FP_test
```

```{r}
#arange the labels on top
      FP_test<-mutate(FP_test, top_row = 0)
      FP_test[14,12] = 1
      FP_test <- arrange(FP_test,order)
FP_test
    # plot the left side of the plot 
      FP_test_L <- FP_test %>% 
        ggplot(aes(y = reorder(Variable, -order))) +
        geom_text(aes(x = 0, label = Variable), hjust = 0, fontface = "bold")+
        geom_text(aes(x = 1, label = estimate_lab),
        hjust = 0,
        fontface = ifelse(FP_test$estimate_lab == "Odds Ratio (95% CI)", "bold","plain")) +
        theme_void() +
        coord_cartesian(ylim = c(1,length(FP_test$Variable) + 1), xlim = c(0, 4))

FP_test_L

FP_test_R <-  
      FP_test |>
      ggplot() +
        geom_text(aes(x = 0, y = reorder(Variable, -order), label = p.adjusted_fig), hjust = 0,
        fontface = ifelse(FP_test$p.adjusted_fig == "p value", "bold", "plain")) +
        theme_void() +
        coord_cartesian(ylim = c(1,length(FP_test$Variable) + 1))

FP_test
```

```{r}
library("patchwork")

layout <- c(
  patchwork::area(t = 0, l = 0, b = 30, r = 25),
  patchwork::area(t = 0, l = 14, b = 30, r = 25),
  patchwork::area(t = 0, l = 23, b = 30, r = 30) 
  )

FP_test_L + FP_test_m + FP_test_R + plot_layout(design = layout)

>>>>

@@

## Vector of categorical variables that need transformation
catVars <- c("Some_College", "Female" , "Married", "White",
             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D", "Substance_D" ,        
             "Psychotic_D", "Other", "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
             "Substance_C", "Other_C" , "No_Co"
             )
## Create a TableOne object
table1_tab_dep <- CreateTableOne(vars = table1_vars_dep, data = Vars_dep,strata ="Depression_Responder",  factorVars = catVars)
table1_tab_dep <- print(table1_tab_dep, formatOptions = list(big.mark = ","))
table1_tab_dep <-data.frame(table1_tab_dep)
table1_tab_dep

@@

# Depression Lasso 
Preparing data for lasso - depression
```{r}
Mothership_lasso_dep <- Mothership_lasso |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(Depression_Responder)
  )

Vars_dep <- Mothership_lasso_dep |>
  select( c(
    Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, 
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, 
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, #Substance_D, #Psychotic_D,  
    #Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre,
    # RDQ
    rdqPOST_coping:rdqPOST_wbs
  ))

@@

# Fit the final model on the training data
model.min <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
                lambda = cv.lasso.dep$lambda.min)

@@

### Final relaxed lasso- Depression
Minimum- 
```{r}
## install.packages("fuzzySim")
library(fuzzySim) ## For FDR adjusted p values
library(broom) # for tidy regression output
```

```{r}
## min model
  glm_min_dep <-
            glm(
      #Outcome varaible
        Depression_Responder ~
      # predictors
        Days_complete_1 + Days_not_attended_1 + Mood_C + CUDOS_pre +
        CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
      #data
        data = Vars_dep,
      # type of regression : logistic = binary / binomial
        family = "binomial")

####### JT - substance disorder seperate    
  # glm(
  #     #Outcome varaible
  #       Depression_Responder ~
  #     # predictors
  #       Age_1 + Some_College + Married + White + Days_complete_1 +  
  #       Mood_D + Substance_D + Mood_C + Substance_C + CUDOS_pre + 
  #       CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
  #     #data
  #       data = Vars_dep,
  #     # type of regression : logistic = binary / binomial
  #       family = "binomial")

###### JT + substance in other
      # glm(
      # #Outcome varaible
      #   Depression_Responder ~
      # # predictors
      #   Days_complete_1 + Days_not_attended_1 + Other + Mood_C + CUDOS_pre +
      #   CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
      # #data
      #   data = Vars_dep,
      # # type of regression : logistic = binary / binomial
      #   family = "binomial")
##############

@@

# Left join the FDR adjusted p.value
FP.min.dep <- left_join(FP.min.dep,ADJ.p.values.min.dep, by = join_by(p.values == p.value))
FP.min.dep$OR = round(as.numeric(FP.min.dep$OR),3)
FP.min.dep$OR_low = round(as.numeric(FP.min.dep$OR_low),3)
FP.min.dep$OR_high = round(as.numeric(FP.min.dep$OR_high),3)
FP.min.dep$p.values = round(as.numeric(FP.min.dep$p.values),3)
FP.min.dep$p.adjusted = round(as.numeric(FP.min.dep$p.adjusted),3)
FP.min.dep$type = c("Depression")
FP.min.dep

write_csv(FP.min.dep, "~/Downloads/FP.min.dep")
```
1se -
```{r}

@@

Vars_anx <- Mothership_lasso_anx |>
  select( c(
    Anxiety_Responder,
    # Demographics
    Age_1,Some_College:Married,White, 
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, 
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, 
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs
  ))

@@

## min model
  glm_min_anx <-  
      glm(
      #Outcome varaible
        Anxiety_Responder ~ 
      # predictors
        Age_1 + Married + Days_complete_1 + Days_not_attended_1 +
        Anxiety_D + Trauma_D +  BPD_Co_C + 
        rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
      #data
      data = Vars_anx, 
      # type of regression : logistic = binary / binomial
      family = "binomial")

####### JT - wo/Substance_D
  # glm_min_anx <-  
  #     glm(
  #     #Outcome varaible
  #       Anxiety_Responder ~ 
  #     # predictors
  #       Age_1 + Married + Days_complete_1 + Days_not_attended_1 + 
  #       Anxiety_D + Trauma_D + BPD_Co_C +
  #       rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
  #     #data
  #     data = Vars_anx, 
  #     # type of regression : logistic = binary / binomial
  #     family = "binomial")
# Summary of the model
  summary.min.anx      <- summary(glm_min_anx)

@@

# Left join the FDR adjusted p.value and round
FP.min.anx <- left_join(FP.min.anx,ADJ.p.values.min.anx, by = join_by(p.values == p.value))
FP.min.anx$p.values = round(as.numeric(FP.min.anx$p.values),3)
FP.min.anx$p.adjusted = round(as.numeric(FP.min.anx$p.adjusted),3)
FP.min.anx$type = c("Anxiety")
FP.min.anx

@@

Anxiety Plot
```{r}
#Create order varaible in dataset to keep it the same as the regression

FP_anx <- read_csv("~/Downloads/FP.min.anx")

#Change the names of variables
FP_anx$Variable

FP_anx$order = c(seq(from=2, to=length(FP_anx$Variable) + 1,1))

FP_anx <- FP_anx |>
  mutate(
    sig = ifelse(p.adjusted <= 0.05, 16,1)
  )
FP_anx

FP_anx$Variable = c(
                    "Age", "Married", "Days Completed", "Days Not Attended", 
                    "Anxiety Disorder", "Trauma Disorder", "Co-Occuring BPD",
                    "Coping Ability", "Positive Mental Health", "Functioning", 
                    "Sense of Well Being"
                    )

FP_anx_m <- FP_anx |>
  ggplot(aes(y = reorder(Variable, -order), color = as.factor(sig))) +
  #take away background
  theme_classic() +
  #make the forrest plot
  geom_point(aes(x=OR), shape= FP_anx$sig,
               # ifelse(FP_anx$p.adjusted <= 0.05, 
               #                        16, # colored ones for significant varaibles
               #                        1), # uncolored ones for insignificant varaibles
             size=4,show.legend = FALSE) +
  geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = .4, show.legend = FALSE) +
  geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.35, show.legend = FALSE)+
  scale_color_manual(values = c("darkgrey","red"))+
  #change x axis name
  labs(
    x="Odds Ratio") +
    # title = "Odds of Anxiety Treatment Non-Response",
    # subtitle = "Based on Pre/Post CUXOS Scores in PHP program") +
  #adjust the dimentions. 
  coord_cartesian(ylim = c(1,length(FP_anx$Variable) + 1)) +
  #add a line at 1 for reference 
   geom_vline(xintercept = 1, linetype="dashed", alpha = .5) +
  #add anotations to help suggests what each side means.
  annotate("text", x = .75, y = length(FP_anx$Variable) + 1, label = "Less Likely", size= 3) +
  annotate("text", x = 1.25, y = length(FP_anx$Variable) + 1, label = "More Likely",size= 3) +
  #Git rid of the Y - Axis
    theme(axis.line.y = element_blank(),
        axis.ticks.y= element_blank(),
        axis.text.y= element_blank(),
        axis.title.y= element_blank())

FP_anx_m

FP_anx <- FP_anx |>
  # round estimates and 95% CIs to 2 decimal places for journal specifications
  mutate(across(
    c(OR, OR_low, OR_high),
    ~ str_pad(
      round(.x, 2),
      width = 4,
      pad = "0",
      side = "right"
    )
  ),
  # add an "-" between HR estimate confidence intervals
  estimate_lab = paste0(OR, " (", OR_low, "-", OR_high, ")")) |>
  # round p-values to two decimal places, except in cases where p < .001
  mutate(p.adjusted_fig = case_when(
    p.adjusted < .001 ~ "<0.001",
    round(p.adjusted, 2) == .05 ~ as.character(round(p.adjusted,3)),
    p.adjusted < .01 ~ str_pad( # if less than .01, go one more decimal place
      as.character(round(p.adjusted, 3)),
      width = 4,
      pad = "0",
      side = "right"
    ),
    TRUE ~ str_pad( # otherwise just round to 2 decimal places and pad string so that .2 reads as 0.20
      as.character(round(p.adjusted, 2)),
      width = 4,
      pad = "0",
      side = "right"
    )
  )) |>
  # add a row of data that are actually column names which will be shown on the plot in the next step
  bind_rows(
    data.frame(
      Variable = "Variable",
      estimate_lab = "Odds Ratio (95% CI)",
      OR_low = "",
      OR_high = "",
      p.adjusted_fig = "p value"
    )
  )

FP_anx[length(FP_anx$Variable),8] = 1
FP_anx

#arange the labels on top
      FP_anx<-mutate(FP_anx, top_row = 0)
      FP_anx[length(FP_anx$Variable),12] = 1
      FP_anx <- arrange(FP_anx,order)
FP_anx
    # plot the left side of the plot 
      FP_anx_L <- FP_anx %>% 
        ggplot(aes(y = reorder(Variable, -order))) +
        geom_text(aes(x = 0, label = Variable), hjust = 0, fontface = "bold")+
        geom_text(aes(x = 1, label = estimate_lab),
        hjust = 0,
        fontface = ifelse(FP_anx$estimate_lab == "Odds Ratio (95% CI)", "bold","plain")) +
        theme_void() +
        coord_cartesian(ylim = c(1,length(FP_anx$Variable)), xlim = c(0, 4))

FP_anx_L

FP_anx_R <-  
      FP_anx |>
      ggplot() +
        geom_text(aes(x = 0, y = reorder(Variable, -order), label = p.adjusted_fig), hjust = 0,
        fontface = ifelse(FP_anx$p.adjusted_fig == "p value", "bold", "plain")) +
        theme_void() +
        coord_cartesian(ylim = c(1,length(FP_anx$Variable)))

FP_anx

library("patchwork")

layout <- c(
  patchwork::area(t = 0, l = 0, b = 30, r = 30),
  patchwork::area(t = 0, l = 15, b = 30, r = 25),
  patchwork::area(t = 0, l = 22, b = 30, r = 30) 
  )

FP_anx_L + FP_anx_m + FP_anx_R + plot_layout(design = layout)

```
## Depression Plot
```{r}
#Create order varaible in dataset to keep it the same as the regression

FP_dep <- read_csv("~/Downloads/FP.min.dep")

#rename the variables for the figure
FP_dep$Variable = c(
                    "Days Completed", "Days Not Attended", 
                    "Co-Ocurring Mood Disorder", "CUXOS Pre-Score", "CUDOS Pre-Score",
                    "Coping Ability", "Positive Mental Health", "Functioning", 
                    "Sense of Well Being"
                    )

FP_dep$order = c(seq(from=2, to=length(FP_dep$Variable) + 1,1))

FP_dep <- FP_dep |>
  mutate(
    sig = ifelse(p.adjusted <= 0.05, 16,1)
  )
FP_dep

FP_dep_m <- FP_dep |>
  ggplot(aes(y = reorder(Variable, -order), color = as.factor(sig))) +
  #take away background
  theme_classic() +
  #make the forrest plot
  geom_point(aes(x=OR), shape= FP_dep$sig,
               # ifelse(FP_dep$p.adjusted <= 0.05, 
               #                        16, # colored ones for significant varaibles
               #                        1), # uncolored ones for insignificant varaibles
             size=4,show.legend = FALSE) +
  geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = .4, show.legend = FALSE) +
  geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.35, show.legend = FALSE)+
  scale_color_manual(values = c("darkgrey","blue"))+
  #change x axis name
  labs(
    x="Odds Ratio") +
    # title = "Odds of Anxiety Treatment Non-Response",
    # subtitle = "Based on Pre/Post CUXOS Scores in PHP program") +
  #adjust the dimentions. 
  coord_cartesian(ylim = c(1,length(FP_dep$Variable) + 1)) +
  #add a line at 1 for reference 
   geom_vline(xintercept = 1, linetype="dashed", alpha = .5) +
  #add anotations to help suggests what each side means.
  annotate("text", x = .8, y = length(FP_dep$Variable) + 1, label = "Less Likely", size= 4) +
  annotate("text", x = 1.2, y = length(FP_dep$Variable) + 1, label = "More Likely",size= 4) +
  #Git rid of the Y - Axis
    theme(axis.line.y = element_blank(),
        axis.ticks.y= element_blank(),
        axis.text.y= element_blank(),
        axis.title.y= element_blank())

FP_dep_m

FP_dep <- FP_dep |>
  # round estimates and 95% CIs to 2 decimal places for journal specifications
  mutate(across(
    c(OR, OR_low, OR_high),
    ~ str_pad(
      round(.x, 2),
      width = 4,
      pad = "0",
      side = "right"
    )
  ),
  # add an "-" between HR estimate confidence intervals
  estimate_lab = paste0(OR, " (", OR_low, "-", OR_high, ")")) |>
  # round p-values to two decimal places, except in cases where p < .001
  mutate(p.adjusted_fig = case_when(
    p.adjusted < .001 ~ "<0.001",
    round(p.adjusted, 2) == .05 ~ as.character(round(p.adjusted,3)),
    p.adjusted < .01 ~ str_pad( # if less than .01, go one more decimal place
      as.character(round(p.adjusted, 3)),
      width = 4,
      pad = "0",
      side = "right"
    ),
    TRUE ~ str_pad( # otherwise just round to 2 decimal places and pad string so that .2 reads as 0.20
      as.character(round(p.adjusted, 2)),
      width = 4,
      pad = "0",
      side = "right"
    )
  )) |>
  # add a row of data that are actually column names which will be shown on the plot in the next step
  bind_rows(
    data.frame(
      Variable = "Variable",
      estimate_lab = "Odds Ratio (95% CI)",
      OR_low = "",
      OR_high = "",
      p.adjusted_fig = "p value"
    )
  )

FP_dep[length(FP_dep$Variable),8] = 1
FP_dep

#arange the labels on top
      FP_dep<-mutate(FP_dep, top_row = 0)
      FP_dep[length(FP_dep$Variable),12] = 1
      FP_dep <- arrange(FP_dep,order)
FP_dep
    # plot the left side of the plot 
      FP_dep_L <- FP_dep %>% 
        ggplot(aes(y = reorder(Variable, -order))) +
        geom_text(aes(x = 0, label = Variable), hjust = 0, fontface = "bold")+
        geom_text(aes(x = 1, label = estimate_lab),
        hjust = 0,
        fontface = ifelse(FP_dep$estimate_lab == "Odds Ratio (95% CI)", "bold","plain")) +
        theme_void() +
        coord_cartesian(ylim = c(1,length(FP_dep$Variable)), xlim = c(0, 4))

FP_dep_L

FP_dep_R <-  
      FP_dep |>
      ggplot() +
        geom_text(aes(x = 0, y = reorder(Variable, -order), label = p.adjusted_fig), hjust = 0,
        fontface = ifelse(FP_dep$p.adjusted_fig == "p value", "bold", "plain")) +
        theme_void() +
        coord_cartesian(ylim = c(1,length(FP_dep$Variable)))

FP_dep

library("patchwork")

layout <- c(
  patchwork::area(t = 0, l = 0, b = 30, r = 30),
  patchwork::area(t = 0, l = 15, b = 30, r = 25),
  patchwork::area(t = 0, l = 22, b = 30, r = 30) 
  )

FP_dep_L + FP_dep_m + FP_dep_R + plot_layout(design = layout)
```
